---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FIBIONsummary

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of FIBIONsummary is to aggregate the csv files from data collected with FIBION devices.

## Installation

You can install the development version of FIBIONsummary like so: 

``` r
devtools::install_github("jhmigueles/FIBIONsummary")
```

## Example

To run the application:

```{r example}
library(FIBIONsummary)
FIBIONsummary::run_app()
```


Please note that the FIBIONsummary project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
